Water Management

### 2020-01-16 Paper/paper.tex
merge changes

@@

	\subsection{Background}
In this work, we want to examine the variations in use of a (hypothetical) water reservoir. Water management of reservoir lakes poses a non trivial task. Different stakeholders have different interests in how to use the water and as lakes usually are public goods, claims of all parties shall be considered. As climate change proceeds, rainfall as the natural influx of lakes becomes more volatile and prolonged dry periods will make water an even more precious resource than it is today. Therefore, the optimal allocation of the available water will be of increasing importance in the future.

@@

	\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

		\bibitem[Figueredo and Wolf, 2009]{Figueredo:2009dg}
		Figueredo, A.~J. and Wolf, P. S.~A. (2009).
		\newblock Assortative pairing and life history strategy - a cross-cultural
		study.
		\newblock {\em Human Nature}, 20:317--330.

	\end{thebibliography}

>>>>

\usepackage{graphicx} % for figures

\usepackage{longtable}

% packages used for citations
\usepackage[
backend=biber,
style=alphabetic,
citestyle=authoryear,
natbib=true
]{biblatex}
\addbibresource{collection.bib}

@@

	\subsection{Motivation}
With world population expected to hit 9.7 billion in 2050 and 11.2 billion in 2100, more and more people have to be fed, which will increase the demand of water for agriculture uses \citep{un2019}. Already today, around one third of the world's population live under physical water scarcity \citep{vorosmarty2000global, alcamo2003global, oki2006global}. With climate change proceeding, rainfall as the natural influx of lakes will become more volatile in some regions while prolonged dry periods will make water an even more precious resource in other areas \citep{guhathakurta2011impact}. This situation will get even worse due to the projected increase in the demand of water per capita in many regions of the world, driven by lifestyle factors, especially diet \citep{vorosmarty2000global}. Despite all those challenges, research suggests that just by using water more efficiently, we will be able to meet the acute water, environment and poverty challenges facing us over the next 50 years \citep{molden2013water}.
Therefore, the optimal allocation and sustainable use of the available water will be of increasing importance in the future.

@@

	\printbibliography
